\documentclass[a4paper]{cv-style}
\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut

\usepackage{hyperref}
\hypersetup{colorlinks=false}

\begin{document}

\header{Bruno}{Benkel}
\lastupdated

% === SIDEBAR ===========================================================================
\begin{aside}
    \section{\href{https://bleaktwig.github.io/cv/}{Web version}}
    \section{Contact}
        Plaza Vergara 142 D51,
        Vi\~na del Mar 2571519
        Chile
        ~
        (+56) 9 8661 4969
        ~
        \href{mailto:bruno.benkel@gmail.com}{bruno.benkel
        @gmail.com}
        ~
        \href{https://github.com/bleaktwig}{github.com/bleaktwig}
    %
    \section{Languages}
        \textbf{Native or Bilingual}:
        Spanish, English
        ~
        \textbf{Elementary}:
        Italian, Norwegian, Chinese
    %
    \section{Programming}
        \textbf{Expert}:
        C, Python, Java
        ~
        \textbf{Proficient}:
        Bash, C++, Haskell
        ~
        \textbf{Elementary}:
        JS, MIPS Assembly, R
    %
    \section{Tools \& Libraries}
        Linux
        Git
        ROOT
        \LaTeX{}
        QT + PySide2
    %
\end{aside}

% === WORK EXPERIENCE ===================================================================
\section{Experience}
    \begin{entrylist}
        \entry
            {2018--Now}
            {CCTVal}
            {Valpara\'iso, Chile}
            {\jobtitle{R\&D Computer Engineer}
            \begin{itemize}
                \item Developer of standard HEP data analysis tools used in Run-Group E.
                \item Head of the Forward Micromegas Tracker alignment team.
                \item Head of the Drift Chambers offline reconstruction optimization team.
                \item Lead developer of the configuration, calibration, alarms, and front-end mechanical ventilator software systems.
                \item Blockchain developer for small-scale energy democratization project.
            \end{itemize}} \\
        \entry
            {2020}
            {Upwork}
            {Remote}
            {\jobtitle{Freelance Software Developer}
            \begin{itemize}
                \item Software developer in IoT and electroencephalography processing software.
                \item Various side-jobs in web development, mainly focused in front-end and UX design work.
            \end{itemize}} \\
        \entry
            {2016--2018}
            {UTFSM}
            {Valpara\'iso, Chile}
            {\jobtitle{Computer Architecture UTA}
            \begin{itemize}
                \item Head of course's teaching assistants.
                \item Teacher of weekly classes in tandem with the course's professor.
                \item Designer, supervisor, and evaluator of monthly hardware laboratory experiences and homework.
            \end{itemize}}
    \end{entrylist}
    \begin{entrylist}
        \entry
            {2018}
            {UTFSM}
            {Valpara\'iso, Chile}
            {\jobtitle{Artificial Intelligence UTA}
            \begin{itemize}
                \item Supervisor and evaluator of the final project of the course.
                \item Assistant in test evaluation.
            \end{itemize}} \\
        \entry
            {2017--2018}
            {w/ Ben Tatum}
            {Los Angeles, US}
            {\jobtitle{Field Service Engineer}
            \begin{itemize}
                \item Assistant in electricity and computer network installations at residential and commercial buildings in Los Angeles.
            \end{itemize}}
    \end{entrylist}

% === EDUCATION =========================================================================
\section{Education}
    \begin{entrylist}
        \entry
            {2021--Now}
            {M.Sc. {\normalfont in High Energy Physics}}
            {UTFSM, Chile}
            {\vspace{-0.3cm}}
        \entry
            {2017--2019}
            {Title (M.Sc. equivalent) {\normalfont in Computer Engineering}}
            {UTFSM, Chile}
            {\vspace{-0.3cm}}
        \entry
            {2012--2017}
            {B.Eng. {\normalfont in Computer Engineering}}
            {UTFSM, Chile}
            {\vspace{-0.3cm}}
    \end{entrylist}

% === PUBLICATIONS ======================================================================
\section{Publications}
    \begin{entrylist}
        \entry
            {2022}
            {{\normalfont Co-author in} ~First CLAS12 measurement of DVCS beam-spin asymmetries in the extended valence region}
            {CLAS Collaboration}
            {\vspace{-0.3cm}}
        \entry
            {2022}
            {{\normalfont Co-author in} ~A multidimensional study of the structure function ratio $\sigma_{LT}'\sigma_0$ from hard exclusive pi+ electro-production off protons in the GPD regime}
            {CLAS Collaboration}
            {\vspace{-0.3cm}}
        \entry
            {2022}
            {{\normalfont Co-author in} ~First Measurement of Lambda Electroproduction off Nuclei in the Current and Target Fragmentation Regions}
            {CLAS Collaboration}
            {\vspace{-0.3cm}}
        \entry
            {2022}
            {{\normalfont Co-author in} ~Alignment of the CLAS12 central hybrid tracker with a Kalman Filter \hspace{1.5cm}}
            {CLAS Collabration}
            {\vspace{-0.3cm}}
        \entry
            {2022}
            {{\normalfont Co-author in} ~Observation of Azimuth-Dependent Suppression of Hadron Pairs in Electron Scattering off Nuclei}
            {CLAS Collaboration}
            {\vspace{-0.3cm}}
        \entry
            {2022}
            {{\normalfont Co-author in} ~Exclusive $\pi^-$ Electroproduction off the Neutron in Deuterium in the Resonance Region}
            {CLAS Collaboration}
            {\vspace{-0.3cm}}
        \entry
            {2022}
            {{\normalfont Co-author in} ~Beam-Recoil Transferred Polarization in $K^+Y$ Electroproduction in the Nucleon Resonance Region with CLAS12}
            {CLAS Collaboration}
            {\vspace{-0.3cm}}
    \end{entrylist}

% === INTERESTS =========================================================================
\section{Interests}
    \vspace{-0.2cm}

    \textbf{Professional}. High energy physics, scientific computing, data analysis, blockchain technologies, optimization, heuristic algorithms, machine learning, neural networks.

    \textbf{Personal}. Piano, music production, woodworking, D\&D, worldbuilding, design, juggling.

% =======================================================================================
\end{document}
